Location of Shrimp Farms

### 2021-04-06 data_check/farms_data_check.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we allocated the production per farm (equally if there is no subregional production estimates).

@@

@@

shrimp_farms <- all_farms %>%
  filter(type == "shrimp")

@@

# determine subregions where points are located

shrimp_farms$reg_id <- raster::extract(gadm_latlon, shrimp_farms)

farms_sf <- shrimp_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

# CHN:HKG
# CHN:MAC
# CRI:NIC
# CRI:PAN
# ECU:COL
# GTM:HND
# GTM:MEX
# HND:NIC
# HND:SLV
# IDN:PNG
# IDN:TLS
# IRN:IRQ
# MEX:GTM
# MEX:USA
# MYS:BRN
# MYS:SGP
# MYS:THA
# PER:ECU
# SAU:KWT
# SLV:HND
# THA:MMR
# THA:MYS
# VNM:KHM

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

# join country production to farms by iso3c

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

# get areas with no regional production data and calculate production per farm

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

# combine and check it all matches ok

test <- farms_prod %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

shrimp_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(shrimp_raster_check)

shrimp_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(shrimp_raster + 1))

shrimp_raster_df <- as.data.frame(shrimp_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(shrimp_raster, stat = "sum") # 5094133
sum(shrimp_raster_df$tonnes_production) # 5094133
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
sum(fao$fao_tonnes_production) # 5094133

write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm_updated.csv")

>>>>

---
title: "Data checking"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "03/06/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

@@

by_type <- all_farms %>%
  group_by(type) %>%
  summarise(n()) %>%
  st_drop_geometry()

by_country_type <- all_farms %>%
  st_drop_geometry() %>%
  group_by(iso3c, type) %>%
  summarise(n())

@@

### 2021-04-06 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

Need to add 68 points to existing 1 point (for a total of 69 points)

@@

 - Oysters
  - This states that nearly all oyster license holders are a part of this association:   
  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
  - We will use this as truth: https://oysterssa.com.au/oyster-growers/
  - We will need to place an additional 22 oyster farms in Australia

@@

```{r}
farms_AUS <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "AUS") %>%
  mutate(data_quality = 4)

write.csv(farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 68, data_quality = 4, total_farms = 69)
write.csv(AUS_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_aus.csv"), row.names = FALSE)
```

>>>>

Need to add 45 points to existing 24 point (for a total of 69 points)

@@

 - Oysters
  - This states that nearly all oyster license holders are a part of this association:   
  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
  - We will use this as truth: https://oysterssa.com.au/oyster-growers/
  - We will need to place an additional 23 oyster farms in Australia

@@

```{r}
farms_AUS <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "AUS") %>%
  mutate(data_quality = 4) ## this is an abalone farm

## now we need to add the oyster farms from this map: https://oysterssa.com.au/oyster-growers/
farms_AUS_2 <- data.frame(lat_lon = c("-32.377148325671286, 133.93965198614558", "-34.91844207220454, 137.7783987555795", "-35.77943962962783, 137.77191642975748", "-33.693162657803185, 136.924417900667", "-32.37607854727286, 133.94039259834852", "-32.373416358293625, 133.9357013204693", "-32.80283080755049, 134.1850786971314", "-34.62455022926624, 135.46366166621291", "-33.67979293746246, 136.91678920994693", "-34.551319592404916, 135.3981400818773", "-34.61868048533167, 135.4628853832039", "-32.3774179110106, 133.94079648728368", "-33.71698462803702, 136.90259542838538", "-34.90762372887531, 137.7836548109512", "-34.623471540228394, 135.46192328133426", "-33.67594103960825, 136.92673532055025", "-32.37775541730595, 133.94005795577584", "-34.52175570620221, 135.38834856713308", "-33.677446237574934, 136.92623952576452", "-32.37683026324807, 133.94078430357064", "-34.625125897259146, 135.46296226954271", "-34.61986531053386, 135.46279518888247", "-32.3779085349619, 133.9409211712551")) %>%
  separate(col = lat_lon, sep = ", ", into = c("lat", "lon")) %>% 
  mutate(iso3c = "AUS") %>%
  mutate(data_quality = 4)

all_farms_AUS <- rbind(farms_AUS, farms_AUS_2)

write.csv(all_farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)

all_farms_sf <- st_as_sf(all_farms_AUS, coords = c("lon", "lat"),
                         crs = crs(gadm_latlon), agr = "constant")

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 45, data_quality = 4, total_farms = 69)
write.csv(AUS_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_aus.csv"), row.names = FALSE)
```

### 2021-04-06 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_marine_fish_general_tonnes_per_farm # 864.3575
```

@@

>>>>

avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_marine_fish_general_tonnes_per_farm # 865.6905
```

@@

test <- all_known_farms_final %>%
  filter(iso3c == "GRC") # perfect
```

### 2021-04-06 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

75+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))

@@

http://www.fao.org/fishery/countrysector/naso_colombia/en
 - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, twenty shrimp farms and seven processing plants. All of them employ qualified labour force, made up of professionals and expert technicians in their respective field of work (Minagricultura and ACUANAL, 2002).”

@@

write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))

>>>>

write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))

@@

http://www.fao.org/fishery/countrysector/naso_colombia/en
 - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, **twenty shrimp farms** and seven processing plants. All of them employ qualified labour force, made up of professionals and expert technicians in their respective field of work (Minagricultura and ACUANAL, 2002).”

@@

write_csv(farms_blz_total, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))
